%!TEX root = Thesis.tex

{\bf Po-Cheng Pan} received the B.S. degree in electronics engineering from National Chiao Tung University, Hsinchu, Taiwan, in 2007. 

From 2007, he we working his M.Sc. degree in electronics engineering. From 2009, he is currently pursuing the Ph.D. degree from the Institute of Electronics. He was a visiting scholar in Technical University of Munich in 2014 through DAAD program. His research interests includes analog circuit optimization, and analog circuit layout automaiton and migration. 

{\bf International Journal Papers}
\begin{enumerate}
  \item P.-C. Pan, C.-Y. Chin, H.-M. Chen, T.-C. Chen, C.-C. Lee and J.-C. Lin, ``A Fast Prototyping Framework for Analog Layout Migration with Planar Preservation,'' in \emph{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}, vol.pp, no.99, pp.1---1. 
\end{enumerate}
{\bf International Conference Papers}
\begin{enumerate}
  \item C.-Y. Chin, P.-C. Pan, H.-M. Cheng, T.-C. Chen, and J.-C. Lin, ``Efficient analog layout prototyping by layout reuse with routing preservation,'' in \emph{International Conference on Computer-Aided Design}, Nov. 2013, pp.40---47.
  \item P.-C. Pan, H.-M. Chen and C.-C. Lin, ``PAGE: Parallel agile genetic exploration towards utmost performance for analog circuit design,'' in \emph{Design, Automation and Testing in Europe Conference \& Exhibition}, Mar. 2013, pp.1849---1854.
  \item P.-C. Pan, H.-M. Chen, Y.-K. Cheng, J.~Liu, and W.-Y. Hu, ``Configurable analog routing methodology via technology and design constraint unification,'' in \emph{International Conference on Computer-Aided Design}, Nov. 2012, pp.620---626.
  \item Y.-P. Weng, H.-M. Chen, T.-C. Chen, P.-C. Pan, C.-H. Chen, and W.-Z. Chen, ``Fast analog layout prototyping for nanometer design migration,'' in \emph{International Conference on Computer-Aided Design}, Nov. 2011, pp. 517 -- 522.
  \item K.-H. Meng, P.-C. Pan, and H.-M. Chen, ``Integrated hierarchical synthesis of analog/rf circuits with accurate performance mapping,'' in \emph{International Symposium on Quality Electronic Design}, Mar. 2011, pp.1---8. 
  \item B.-Z. Chen, H.-M. Chen, L.-D. Huang and P.-C. Pan, ``A stochastic-based efficient critical area extractor on OpenAccess platform,'' in \emph{ACM Great Lake symposium on VLSI}, May 2009, pp.197---222.

\end{enumerate}
